Misexpression of germline programs with loss of the X-linked intellectual disability factor KDM5C

### 2024-04-18 submission/manuscript.Rmd
add updated figs to manuscript

>>>>

\begin{figure}
  \centering 
  \includegraphics{../submission/compiled_figs/What_are_germline_genes.pdf}
  \caption[Misexpression of tissue-specific genes, including germline genes, in the \textit{Kdm5c}-KO in the brain]{\textbf{Ovary and testis germline genes are expressed in the \textit{Kdm5c}-KO in the brain.} \textbf{A.} enrichPlot gene ontology (GO) of \textit{Kdm5c}-KO amygdala and hippocampus testis-enriched DEGs \textbf{B.} Expression of testis DEGs in wild-type (WT) testis versus germ cell-depleted (W/Wv) testis. Expression is in Fragments Per Kilobase of transcript per Million mapped reads (FPKM). \textbf{C.} Number of testis DEGs that were classified as cell-type specific markers in a single cell RNA-seq dataset of the testis. Germline cell types are highlighted in green, somatic cell types in black. \textbf{D.} Expression of ovary-enriched DEGs in a wild-type versus germ cell-depleted testis }
  \label{figurelabel}
\end{figure}

\newpage
## Figure outline:
